Trends of SDR in Thessaloniki

### 2023-06-08 Article.Rmd
Commit 2023-06-08 18:17

```{r trendALL, echo=F, fig.cap="Anomaly (\\%) of the daily Global radiation relative to climatological values for 1993 - 2022. The straight black line shows the long term trend for All-sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

@@

\footnotesize
```{r trendtable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("Global" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp) <- NULL
names(pp) <- c("Trend %/year", "Trend p-value", "Sky condition", "Trend statistical significance")

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "\\label{tab:trendtable}Trends of daily means by sky conditions.")
# \\label{tab:tab2}
# knitr::kable(pp, caption = "Trends of daily means by sky conditions.")
```
\normalsize

@@

<!--\tiny -->
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
cat('\n\n\\footnotesize\n\n')
pander::pander(pp,
               caption = "Table of trends and stats")
cat('\n\n\\normalsize\n\n')
```
<!--\normalsize-->

**END**

>>>>

```{r trendALL, echo=F, fig.cap="Anomaly (\\%) of the daily Global radiation relative to climatological values for 1993 - 2023. The straight black line shows the long term trend for All-sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

@@

<!-- \footnotesize -->
```{r trendtable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("Global" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp) <- NULL
names(pp) <- c("Trend %/year", "Trend p-value", "Sky condition", "Trend statistical significance")

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "\\label{tab:trendtable}Trends of daily means by sky conditions.")
# \\label{tab:tab2}
# knitr::kable(pp, caption = "Trends of daily means by sky conditions.")
```
<!-- \normalsize -->

@@

-------------------------------------------------
                   **END**
-------------------------------------------------
